---
title: "Nintendo_Switch_Best_Selling_Games"
author: "Jubayer"
date: "2023-02-01"
output: html_document
---
## Loading Packages
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
```

## Creating Dataset
```{r}
nintendo <- read_csv("D:\\Google Data Analytics\\nintendo\\best_selling.csv")

```
## Top Ten Best Selling Games
```{r}
top_10 <- nintendo %>% 
  arrange(desc(copies_sold)) %>% 
  slice(1:10)
View(top_10)
```

## Visualization of Top 10 Best Selling Games
```{r}
ggplot(top_10, aes(x=title, y=copies_sold/1000000))+
  geom_col(fill="blue")+
  theme(axis.text.x = element_text(size=10, angle = 90))+
  ylab("Sold In Million")+
  xlab("Games")+
  labs(title = "Top 10 Best Selling Games")
```

## Top 5 most Popular Genre 
```{r}
#top 5 most popular genre 
top_5G = aggregate(nintendo$copies_sold, by=list(Genre=nintendo$genre), FUN=sum) %>% 
  arrange(desc(x)) %>% 
  slice(1:5)
```
## Visuallization of Top 5 most Popular Genre
```{r}
ggplot(top_5G, aes(x= Genre, y = x/1000000))+
  geom_col(fill= "Skyblue")+
  theme(axis.text.x = element_text(size=10, angle = 45))+
  ylab("Sold In Million")+
  xlab("Genre")+
  labs(title = "Top five Most Popular Genre")

```

## Total number of copies sold from 2018 to 2022
```{r}
year_data <- nintendo %>% 
  group_by("year" = format(as_of, "%Y")) %>% 
  summarise(Sold= sum(copies_sold))
head(year_data)

```

## Visualization of games sold per year
```{r}
ggplot(year_data, aes(x= year, y= Sold/1000000, group=1))+
  geom_line(color= "green", size=1.2)+
  ylab("Sold In Million")+
  geom_point()+
  labs(title = "Number of Games sold in 2018-2022")
```

## Copies sold by each Developer
```{r}
dev <- nintendo %>% 
  group_by(developer) %>% 
  summarise(copies_sold=sum(copies_sold)) %>% 
  arrange(desc(copies_sold))
dev
```

## Top 5 developer and other developer comparison
```{r}
top5 <- dev %>%
  slice(1:5) #separating top 5

#adding all other developers total copies_sold into one variable 
other <- dev %>%
  slice(6:40) %>% 
  summarise( developer= 'Other developers', copies_sold= sum(copies_sold))
#merging this two information
top_5_and_other <- rbind(top5, other)
head(top_5_and_other)
```

## Pie chart of top 5 and other developers Sales Performance
```{r}
ggplot(top_5_and_other, aes(x = "", y = copies_sold, fill = developer)) +
  geom_col(color = "black") +
  geom_text(aes(label = paste0(round((copies_sold*100)/sum(copies_sold)), "%")),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  scale_fill_brewer() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        panel.background = element_rect(fill = "#ebf2ff"),
        plot.background = element_rect(fill = "#ebf2ff"),
        legend.background = element_rect(fill = "#ebf2ff"))+
  labs(title = "Comparison of Sales Performance by Developers")

```




